Preregistration analysis, Cost 2 study

### 2019-05-13 Cost2/Cost2_prereg.Rmd
pre-post analyses for both Costs. Need pre/post mix logistic for cost 2 now

``` {r 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# pre
t1 <- dataAll %>%
  filter(Choice < 2, Half == "Half_1") %>%
  group_by(SubjID) %>%
  filter(Handling == 10) %>%
  group_by(SubjID, Cost, Reward) %>%
  summarise(pAccept = mean(Choice)) %>%
  group_by(Cost, Reward) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(nSubjs)) %>%
  ungroup() %>%
  mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
  ggplot(aes(Reward, propAccept, color = Cost)) +
    geom_point(size = 3, show.legend = F) +
    geom_line(show.legend = F) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
    labs(y = "Proportion Accepted", title = "First Half") +
    theme(legend.key = element_blank(),
          legend.position = c(0.8, 0.25),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

# post half
t2 <- dataAll %>%
  filter(Choice < 2, Half == "Half_2") %>%
  group_by(SubjID) %>%
  filter(Handling == 10) %>%
  group_by(SubjID, Cost, Reward) %>%
  summarise(pAccept = mean(Choice)) %>%
  group_by(Cost, Reward) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(nSubjs)) %>%
  ungroup() %>%
  mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
  ggplot(aes(Reward, propAccept, color = Cost)) +
    geom_point(size = 3, show.legend = F) +
    geom_line(show.legend = F) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = F) +
    scale_y_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
    labs(y = "", title = "Second Half") +
    theme(legend.position = c(0.8, 0.2),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

grid.arrange(t1, t2, ncol = 2)
```
\bigskip

@@

# now for each first block experienced, how do costs compare per reward x handling
dataAll %>%
  group_by(SubjID) %>%
  mutate(FirstBlock = case_when(
    Handling[1] == 2 ~ "Two",
    Handling[1] == 10 ~ "Ten",
    Handling[1] == 14 ~ "Fourteen",
  )) %>%
  group_by(Cost, Handling, Reward, FirstBlock) %>%
  summarise(pAccept = mean(Choice),
            SE = sd(Choice) / sqrt(length(Choice))) %>%
  ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
    geom_point(size = 3) + 
    geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1) +
    geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
    labs(x = "Reward.Handling", y = "Proportion Accepted") +
    scale_color_manual(values = cols) +
    facet_wrap(vars(FirstBlock), ncol = 3) +
    theme(legend.key = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))
```

>>>>

``` {r 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# # pre
# t1 <- dataAll %>%
#   filter(Choice < 2, Half == "Half_1") %>%
#   group_by(SubjID) %>%
#   filter(Handling == 10) %>%
#   group_by(SubjID, Cost, Reward) %>%
#   summarise(pAccept = mean(Choice)) %>%
#   group_by(Cost, Reward) %>%
#   summarise(propAccept = mean(pAccept),
#             SE = sd(pAccept) / sqrt(nSubjs)) %>%
#   ungroup() %>%
#   mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
#   ggplot(aes(Reward, propAccept, color = Cost)) +
#     geom_point(size = 3, show.legend = F) +
#     geom_line(show.legend = F) +
#     scale_color_manual(values = cols) +
#     scale_fill_manual(values = cols) +
#     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
#     scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
#     labs(y = "Proportion Accepted", title = "First Half") +
#     theme(legend.key = element_blank(),
#           legend.position = c(0.8, 0.25),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))
# 
# # post half
# t2 <- dataAll %>%
#   filter(Choice < 2, Half == "Half_2") %>%
#   group_by(SubjID) %>%
#   filter(Handling == 10) %>%
#   group_by(SubjID, Cost, Reward) %>%
#   summarise(pAccept = mean(Choice)) %>%
#   group_by(Cost, Reward) %>%
#   summarise(propAccept = mean(pAccept),
#             SE = sd(pAccept) / sqrt(nSubjs)) %>%
#   ungroup() %>%
#   mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
#   ggplot(aes(Reward, propAccept, color = Cost)) +
#     geom_point(size = 3, show.legend = F) +
#     geom_line(show.legend = F) +
#     scale_color_manual(values = cols) +
#     scale_fill_manual(values = cols) +
#     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = F) +
#     scale_y_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
#     labs(y = "", title = "Second Half") +
#     theme(legend.position = c(0.8, 0.2),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))
# 
# 
# 
# grid.arrange(t1, t2, ncol = 2)

dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID) %>%
  filter(Handling == 10) %>%
  mutate(Half = ifelse(Half == "Half_1", "First Block", "Last Block")) %>%
  group_by(SubjID, Half, Cost, Reward) %>%
  summarise(pAccept = mean(Choice)) %>%
  group_by(Half, Cost, Reward) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(nSubjs)) %>%
  ungroup() %>%
  mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
  ggplot(aes(Reward, propAccept, color = Cost)) +
    geom_point(size = 3, show.legend = F) +
    geom_line(size = 1, show.legend = F) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
    labs(y = "Proportion Accepted") +
    facet_wrap(vars(Half), ncol = 2) +
    theme(legend.key = element_blank(),
          legend.position = c(0.9, 0.25),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

```
\bigskip

@@

# now for each first block experienced, how do costs compare per reward x handling
dataAll %>%
  group_by(SubjID) %>%
  mutate(FirstBlock = case_when(
    Handling[1] == 2 ~ "Two",
    Handling[1] == 10 ~ "Ten",
    Handling[1] == 14 ~ "Fourteen",
  )) %>%
  group_by(Cost, Handling, Reward, FirstBlock) %>%
  summarise(pAccept = mean(Choice),
            SE = sd(Choice) / sqrt(length(Choice))) %>%
  ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
    geom_point(size = 3) + 
    geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1) +
    geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
    labs(x = "Reward.Handling", y = "Proportion Accepted") +
    scale_color_manual(values = cols) +
    facet_wrap(vars(FirstBlock), ncol = 3) +
    theme(legend.key = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

# # now also separated by half
# dataAll %>%
#   group_by(SubjID) %>%
#   mutate(FirstBlock = case_when(
#     Handling[1] == 2 ~ "Two",
#     Handling[1] == 10 ~ "Ten",
#     Handling[1] == 14 ~ "Fourteen",
#   )) %>%
#   group_by(Cost, Handling, Reward, FirstBlock, Half) %>%
#   summarise(pAccept = mean(Choice),
#             SE = sd(Choice) / sqrt(length(Choice))) %>%
#   ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
#     geom_point(size = 3) + 
#     geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1) +
#     geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
#     labs(x = "Reward.Handling", y = "Proportion Accepted") +
#     scale_color_manual(values = cols) +
#     facet_wrap(vars(Half, FirstBlock), ncol = 3) +
#     theme(legend.key = element_blank(),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))
```
